---
output: github_document
eval: FALSE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# timely

<!-- badges: start -->
[![R-CMD-check](https://github.com/meyerkn00/timely/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/meyerkn00/timely/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of timely is to simplify the creation of filenames when using functions such as write_csv() or write_dta(). It provides one function, timely(), which does so.

## Installation

You can install the development version of timely from [GitHub](https://github.com/timely) with:

``` {r}
# install.packages("devtools")
devtools::install_github("meyerkn00/timely")
```

## Example

When working with data in R, the time comes to output the data into a file. Writing that filename should be trivial, but once one considers adding a timestamp the code becomes more complicated than one would like:
```{r}
paste0("iris", "_", format(Sys.time(), format = "%m%d%y_%H.%M"), ".csv")
```

The result, "iris_111123_11.00.csv", is reached, but remembering to copy-paste and edit this every time one wants to write an output file is tedious.

That is where timely() comes in.

The same operation using timely() is done as follows:

```{r}
library(timely)

timely("iris", "csv")
```

By making some base assumptions (such as the standard date/time format of mdy_H.M) allows this operation to be completed with fewer keystrokes and less effort.
timely() is built on format() so that one can specify non-default time formats using that syntax. This function can be used within functions like write.csv() and haven::write_dta() to create filenames.

## Please note:

Currently this project is written for the use of the developer. As such, the timezone is not specified and the time/date format defaults to North American structure (e.g. month/date/year). If you would like different defaults supported, please reach out at karl@themeyers.org and let me know.
