---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timely

<!-- badges: start -->
<!-- badges: end -->

The goal of timely is to simplify the creation of filenames when using functions such as write_csv() or write_dta(). It provides one function, timely(), which does so.

## Installation

You can install the development version of timely from [GitHub](https://github.com/timely) with:

``` {r}
# install.packages("devtools")
devtools::install_github("meyerkn00/timely")
```

## Example

When working with data in R, the time comes to output the data into a file. Writing that filename should be trivial, but once one considers adding a timestamp the code becomes more complicated than one would like:
```{r}
data(iris)
write.csv(paste0("iris", "_", format(Sys.time(), format="%m%d%y_%H.%M"), ".csv"))
```

The result, "iris_111123_11.00.csv", is reached, but remembering to copy-paste and edit this every time one wants to write an output file is tedious.

That is where timely() comes in.

The same operation in using timely() is as follows:

```{r}
library(timely)

data(iris)
write.csv(iris, timely("iris", "csv"))
```

By making some base assumptions (such as the standard date/time format of mdy_H.M) allows this operation to be completed with fewer keystrokes and less effort.
timely() is built on format() so that one can specify non-default time formats using that syntax.

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.
